---
title       : Visualize Your Blood Pressure Results
subtitle    : Interact and interpret blood pressure readings 
author      : kjco  9/20/2014
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What do your blood pressure results mean?
<br>
#### Systolic and Diastolic Blood Pressure
* The systolic reading measures the pressure in the arteries when the heart beats.
* The diastolic reading measures the pressure in the arteries between heartbeats.
* Often represented as Systolic/Diastolic mmHg (eg. 120/80 mmHg)

<br>
#### Normal vs. High Blood Pressure
* A normal blood pressure range is less than 120/80 mmHg.
* The American Heart Association defines over 140/90 mmHg as High Blood Pressure.

--- .class #id 

## Are there factors that influence blood pressure?

### Male or Female?

```{r plot gender diff 2, echo=FALSE}
bp2 <- read.csv(file="./bloodpressure.csv",header=TRUE)

library(ggplot2)
p3 <- ggplot(bp2, aes(x=BPXSY, fill=RIAGENDR, name="Gender")) +
    xlab("Systolic Blood Pressure (mm Hg)") +
    geom_histogram(binwidth=2, alpha=.5, position="identity")
p3

```

---

## How do your results compare?
* Visualize and compare your results to a population of the same gender and age range.
* Get the calculated percentile of your results in this population.
  - Your systolic blood pressure is at the 32 percentile of Females age 30 to 40.

```{r example app, echo=FALSE}

library(ggplot2)
p1 <- ggplot(bp2, aes(x=BPXSY))
p1 <- p1 + geom_histogram(aes(y=..density..),colour = "darkgreen",fill = "white",
                         binwidth = 3) +
  xlab("Systolic Blood Pressure (mm Hg)") +
  geom_vline(aes(xintercept=140),colour="red",linetype="dashed",size=1) +
  geom_vline(aes(xintercept=110),colour="blue",size=1)
p1

```


---

## Visualize, Compare, and Interact 

<br>

#### Goals
* Understand and interpret your own blood pressure results.
* Gauge the distribution of blood pressures across different populations of gender and age.
* See where you land in this distribution.

<br>
##### Information

* Population blood pressure data source: 
National Health and Nutrition Examination Survey (NHANES) 2011-2012.

* Go to [Visualize Your Blood Pressure Results] shiny webapp!

[Visualize Your Blood Pressure Results]:https://kjco.shinyapps.io/visbp/


